Towards atomistic resolution structure of phosphatidylcholine glycerol backbone and choline headgroup at different ambient conditions\footnote{Publication about results presented in the NMRlipids project}

### 2015-03-22 HGmodelMANUSCRIPT/HGmodel_ACStemplate.tex
add Acknowledgements
Contributions of Marius Retegan

MJ and JT acknowledge and CSC - IT Center for Science for computational resources (project number tty3979).
MJ also acknowledges the Finnish Doctoral Programme in Computational Sciences (FICS) for funding.

\end{acknowledgement}

@@

\subsection{Author Contributions}
\todo{Please write a text summarizing your contribution} \\
{\it Alexandru Botan} \\
{\it Fernando Favela}  \\
{\it Patrick Fuchs} \\
{\it Matti Javanainen} prepared and performed simulations with multiple lipid models and analyzed the results. Supervised the work of JT.\\
{\it Waldemar Kulig} prepared the MD simulations with cholesterol for the MacRog FF \\
{\it Antti Lamberg}  \\
{\it Markus S. Miettinen}  \\
{\it Luca Monticelli}  \\
{\it Jukka Maatta}  \\
{\it O. H. Samuli Ollila} Designed and managed the work. Ran and analyzed several simulations. Wrote the manuscript.  \\
{\it Marius Retegan}  \\
{\it Tomasz Rog}  \\
{\it Hubert Santuz}  \\
{\it Joona Tynkkynen} prepared and performed the dehydration simulations with the MacRog FF.\\

>>>>

MJ and JT acknowledge and CSC - IT Center for Science for computational resources (project number tty3979).
MJ also acknowledges the Finnish Doctoral Programme in Computational Sciences (FICS) for funding.
JT, MJ, TR and WK acknowledge the funding from the Academy of Finland (Centre of Excellence program) 
and the European Research Council (Advanced Grant project CROWDED-PRO-LIPIDS).
\end{acknowledgement}

@@

\subsection{Author Contributions}
\todo{Please write a text summarizing your contribution} \\
{\it Alexandru Botan} \\
{\it Fernando Favela}  \\
{\it Patrick Fuchs} \\
{\it Matti Javanainen} prepared and performed simulations with multiple lipid models and analyzed the results. Supervised the work of JT.\\
{\it Waldemar Kulig} prepared the MD simulations with cholesterol for the MacRog FF \\
{\it Antti Lamberg}  \\
{\it Markus S. Miettinen}  \\
{\it Luca Monticelli}  \\
{\it Jukka Maatta}  \\
{\it O. H. Samuli Ollila} Designed and managed the work. Ran and analyzed several simulations. Wrote the manuscript.  \\
{\it Marius Retegan} Prepared and validated the GROMACS compatible parameter files for GAFFlipid and Lipid14 force fields.\\
{\it Tomasz Rog}  \\
{\it Hubert Santuz}  \\
{\it Joona Tynkkynen} prepared and performed the dehydration simulations with the MacRog FF.\\
